### 2023-12-13 latex/Plusone_configs/paper.tex
#26 Paper

\subsubsection*{2.1 XGBoost}
 The concept of boosting, proposed by Freund and Schapire (1999), revolves around an ensemble model strategy that combines multiple weak learners to create a more robust learner. Friedman (1999) introduced Gradient Tree Boosting, an improvement in boosting that incorporates the gradient descent algorithm into the loss function to minimize errors. Expanding on gradient boosting, Chen and Guestrin (2016) introduce XGBoost, a scalable end-to-end tree boosting system based on additive training strategy that augments gradient tree boosting with regularization, efficient handling of sparse data, and enhanced computational efficiency, resulting in superior speed and accuracy. Eq.1 denotes the objective function of XGBoost where \(\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}\) represents the training loss function and \(\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}\) denotes the complexity of trees.
\begin{eqnarray}
\label{eq:schemeP}
\mathrm{Obj}=\underbrace{\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}}_{Training \: Loss} +\underbrace{\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}}_{Complexity \: of \: trees}
\end{eqnarray}

>>>>

\subsubsection*{2.1 XGBoost}
 The concept of boosting, proposed by Freund and Schapire (1999), revolves around an ensemble model strategy that combines multiple weak learners to create a more robust learner. Friedman (1999) introduced Gradient Tree Boosting, an improvement in boosting that incorporates the gradient descent algorithm into the loss function to minimize errors. Expanding on gradient boosting, Chen and Guestrin (2016) introduce XGBoost, a scalable end-to-end tree boosting system based on additive training strategy that augments gradient tree boosting with regularization, efficient handling of sparse data, and enhanced computational efficiency, resulting in superior speed and accuracy. Eq.8 denotes the general objective function of XGBoost where \(\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}\) represents the training loss and \(\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}\) denotes the complexity of trees.
\begin{eqnarray}
\label{eq:schemeP}
\mathrm{Obj}=\underbrace{\mathbf{\sum_{i=1}^{n}l(y_i,\hat{y}_i)}}_{Training \: Loss} +\underbrace{\mathbf{{\sum_{k=1}^{K}}\Omega(f_k)}}_{Complexity \: of \: trees}
\end{eqnarray}
